Evaluating Class Imbalance

### 2019-06-12 Scripts/evaluating_imbalance_ratios.Rmd
edits

      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1])

>>>>

      ir.per.chr <- rbind(ir.per.chr, table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[1]/table(mcols(binslist_dat_center[seqnames(binslist_dat_center)==chrs[k]])$y)[2])
